preciseTAD: A machine learning framework for precise 3D domain boundary prediction at base-level resolution

### 2020-09-22 Manuscript/manuscript.Rmd
shortened fig3 title per journal requirements

![**Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yield optimal TAD boundary region predictive performance for GM12878 Arrowhead TAD boundaries.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)

@@

**Supplementary Figure 3. Distance-type predictors combined with random under-sampling at 5 kb resolution genomic bins yield optimal boundary region predictive performance.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562. (B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.

>>>>

![**Determining optimal data level characteristics for building TAD boundary region prediction models on GM12878.** Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate standard deviation from the mean performance across each holdout chromosome used for testing.](Figures/figure3.png)

@@

**Supplementary Figure 3. Determining optimal data level characteristics for building TAD boundary region prediction models on K562.** (A) Averaged balanced accuracies are compared across resolution, within each predictor-type: Signal, OC, OP, and Distance, and across resampling techniques: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple) when using Arrowhead ground truth boundaries for K562. (B) Averaged balanced accuracies are compared for GM12878 and (C) K562  within each predictor-type: Signal, OC, OP, and Distance, and across resampling technique: no resampling (None; red), random over-sampling (ROS; green), random under-sampling (RUS; blue), and synthetic minority over-sampling (SMOTE; purple). Error bars indicate standard deviation away from the mean performance across each holdout chromosome used for testing.
